Report - Latest Rodent Data

### 2017-11-14 report.Rmd

---
title: "Report - September 2017"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")
library(portalr)

# get most recent rodent data
rodents = abundance("repo", shape='flat')
period_code = max(rodents$period)
observed = dplyr::filter(rodents, period == period_code)

# get new moon number associated with this period
newmoons_table = read.csv(text = getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))
moon_code = dplyr::filter(newmoons_table,period==period_code) %>% select(newmoonnumber) %>% as.integer()

# get most recent forecast prior to data collection -- WIP!!!!!!!! there's an issue up
data = read.csv('predictions/2017-06-23Allforecasts.csv',na.strings = '')
data = plyr::rename(data,c('NewMoonNumber' = 'newmoonnumber'))

>>>>

---
title: "Report - Latest Rodent Data"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")
library(portalr)

# get most recent rodent data
rodents = abundance("repo", shape='flat')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period)

# get new moon number associated with this period
newmoons_table = read.csv(text = getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))
newmoons_table$censusdate = as.Date(newmoons_table$censusdate,format='%Y-%m-%d')
moon_code = dplyr::filter(newmoons_table,period==most_recent_period) %>% select(newmoonnumber) %>% as.integer()
most_recent_date = dplyr::filter(newmoons_table,period==most_recent_period) %>% dplyr::select(censusdate)

# get most recent forecast prior to data collection
files = data.frame(names = list.files(path = './predictions', pattern = '*Allforecasts.csv'))
files$filedates = as.Date(substr(files$names,1,10),format='%Y-%m-%d')
latest_forecast = dplyr::filter(files,filedates<most_recent_date) %>% tail(1)

data = read.csv(paste('predictions/',latest_forecast$names,sep=''),na.strings = '')
